---
title: "Customer Churn Prediction Using Supervised Machine Learning"
author: "Ethan Andre Dalocanog"
date: "2026-05-30"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Abstract
Provide a concise summary of the study including purpose, methods, results, and conclusions (150–250 words).

# Chapter 1: Introduction

## Background of the Study
Discuss the context and importance of the research problem.

## Statement of the Problem
Clearly state the research questions.

1. What is ...?
2. How does ...?

## Objectives of the Study
### General Objective
- To investigate ...

### Specific Objectives
- To determine ...
- To analyze ...

## Hypotheses (if applicable)
- **H0**: There is no significant relationship between ...
- **H1**: There is a significant relationship between ...

## Significance of the Study
Explain who benefits and how.

## Scope and Limitations
Define the boundaries of the study.


# Chapter 2: Review of Related Literature

## Related Studies
Summarize previous research.

## Related Literature
Discuss theories and concepts.

## Conceptual Framework
(Insert diagram if needed)

```{r conceptual-framework, echo=FALSE}
# Example placeholder
# plot(1:10, 1:10, main="Conceptual Framework (Replace)")
```

## Chapter 3: Methodology
Research Design

Describe the design (e.g., descriptive, experimental).

Data Collection

Get a data set from www.kaggle.com

```{r}
# Load dataset
# data <- read.csv("your_data.csv")
# head(data)
```

Variables Description

Explain dependent and independent variables.

Data Analysis Techniques

- Descriptive Statistics
- Inferential Statistics
- Machine Learning Models (if applicable)

## Chapter 4: Results and Discussion
Descriptive Statistics

```{r}
#summary(data)
```

Visualization
```{r}
library(ggplot2)
#ggplot(data, aes(x=Variable1, y=Variable2)) +
#  geom_point() +
#  theme_minimal()
```

Model (Example: Linear Regression)
```{r}
#model <- lm(Y ~ X1 + X2, data=data)
#summary(model)
```

Interpretation

Discuss findings in paragraph form.

## Chapter 5: Conclusion and Recommendations
Conclusion

Summarize key findings.

**Recommendations**

Provide practical suggestions

## References

Use APA format.

## Appendices
Appendix A: Code